### 2013-03-26 R/reportmd.Rmd
Update to markdown report (bug fixes), added instructions to report.R

```{r echo=FALSE, comment=''}
if("location" %in% sitevarnames){
  sites <- sort(levels(.dat$data[,"location"]))
  cat(paste(sites, collapse="\n"))
}
```

```{r echo=FALSE, fig.width=8, fig.height=6}
if("latitude" %in% sitevarnames){
  latlong <- .dat$data[,c("location","latitude","longitude")]
  latlong <- latlong[!duplicated(latlong$location),]

  suppressPackageStartupMessages(library(maps))

@@

The dataset includes the following species (`r nlevels(.dat$data$species)` species in total):
`r cbind(sort(levels(.dat$data$species)))`

@@

Plot of data
---------------------------------
```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(d$data, "Ishihara0000", pdf=FALSE)
```

>>>>

```{r echo=FALSE, comment=''}
if("location" %in% sitevarnames){
  sites <- sort(unique(as.character(.dat$data[,"location"])))
  cat(paste(sites, collapse="\n"))
}
```

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE}
if("latitude" %in% sitevarnames){
  latlong <- .dat$data[,c("location","latitude","longitude")]
  latlong <- latlong[!duplicated(latlong$location),]

  library(maps)

@@

The dataset includes the following species (`r length(unique(.dat$data$species))` species in total):
`r cbind(sort(unique(as.character(.dat$data$species))))`

@@

Plot of data
---------------------------------
```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(d$data, .study, pdf=FALSE)
```
